Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
figures accordions and slaloms

@@

@@

This construction is illustrated on \fref{fig:examplesSurfaces}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for the quivers~$\bar Q$ of \fref{fig:quivers}. The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces. The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.}
	\label{fig:examplesSurfaces}
\end{figure}

%\begin{figure}[t]
%	\capstart
%	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
%	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}. The boundaries of the surfaces are shaded. The first surface is a cylinder, the second one is a torus with a hole.}
%	\label{fig:examplesSurfaces2}
%\end{figure}
%
Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.

\begin{remark}
We could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
\end{itemize}
\end{remark}

The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

@@

\begin{proposition}
\label{prop:dissectionsAreCellular}
Let~$\bar Q$ be a locally gentle bound quiver.
Then the dissections~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ are cellular and dual to each other.
\end{proposition}
\begin{proof}

\begin{theorem}
\label{thm:bijectionLocallyGentleAndSurfaces}
 Up to isomorphism, the constructions of Definitions \ref{def:quiverDualDissections} and \ref{def:surfaceQuiver} are inverse to each other.
 They induce a bijection between the set of isomorphism classes of locally gentle algebras and the set of homeomorphism classes of marked surfaces with a pair of dual cellular dissections.
\end{theorem}

>>>>

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{accordions}}
	\caption{Some accordions.}
	\label{fig:accordions}
\end{figure}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{slaloms}}
	\caption{Some slaloms.}
	\label{fig:slaloms}
\end{figure}

@@

This construction is illustrated on \fref{fig:surfaces}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{surfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for the quivers~$\bar Q$ of \fref{fig:quivers}. The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces. The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.}
	\label{fig:surfaces}
\end{figure}

Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
\end{itemize}
The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

@@
